%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% possible options include font size ('10pt', '11pt' and '12pt'), paper size
% ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and
% 'landscape') and font family ('sans' and 'roman')
\documentclass[10pt,letterpaper,sans]{moderncv}
\usepackage{xspace}
\newcommand\eat[1]{}

%\newcommand{\ie}{{\it i.e.,}\xspace}

% moderncv themes style options are 'casual' (default), 'classic', 'oldstyle'
% and 'banking'
\moderncvstyle{banking}

% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey'
% and 'black'
\moderncvcolor{blue}

% to set the default font; use '\sfdefault' for the default sans serif font,
% '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}         

% Uncomment for no page numbers
%\nopagenumbers{}                                  

% character encoding: if you are not using xelatex ou lualatex, replace by the
% encoding you are using
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}


\newcommand{\cvdoublecolumn}[2]{%
  \cvitem[0.75em]{}{%
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}%
    \hfill%
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}%
    }%
}

% usage: \cvreference{name}{address line 1}{address line 2}{address line 3}{address line 4}{e-mail address}{phone number}
% Everything but the name is optional
% If \addresssymbol, \emailsymbol or \phonesymbol are specified, they will be used.
% (Per default, \addresssymbol isn't specified, the other two are specified.)
% If you don't like the symbols, remove them from the following code, including the tilde ~ (space).

\newcommand{\cvreference}[7]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4\newline}%
    \ifthenelse{\equal{#5}{}}{}{#5\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
    \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7}}


\makeatletter
\renewcommand\@biblabel[1]{\textbullet}
\renewenvironment{thebibliography}[1]
     {\section*{\refname}%
      \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
      \list{}%
           {\leftmargin0pt
            \@openbib@code
            \usecounter{enumiv}}%
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000%
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
\makeatother

%\usepackage{multibib}
%\newcites{conference,workshop,demos,trs}{{Conferences},{Workshops},{Demos},{Technical Reports}}

% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}

% for the 'classic' style, if you want to force the width allocated to your
% name and avoid line breaks. be careful though, the length is normally
% calculated to avoid any overlap with your personal info; use this at your own
% typographical risks...
%\setlength{\makecvtitlenamewidth}{10cm}

% personal data
\name{Shoumik}{Palkar}
\title{Curriculum Vitae}
\phone[mobile]{+1~(408)~505~6159}
\email{shoumik@cs.stanford.edu}
%\renewcommand*\httplink[2][]{{\urlstyle{sf}\expandafter\href#2}}
\homepage{{https://www.shoumik.xyz}{}}

% optional, remove / comment the lines if not wanted
%\social[linkedin]{john.doe}
\social[twitter]{sppalkia}
\social[github]{sppalkia}
%\extrainfo{additional information}

%'64pt' is the height the picture must be resized to, 0.4pt is the thickness of
%the frame around it (put it to 0pt for no frame) and 'picture' is the name of
%the picture file
%\photo[64pt][0.4pt]{picture}
%\quote{Some quote}

% to show numerical labels in the bibliography (default is to show no labels);
% only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}

\makeatother
\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{conference,workshop,demos,trs}{{Conferences},{Workshops},{Demos},{Technical Reports}}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Research Interests}
Computer systems, big data, machine learning, networking

\section{Education}
\cventry{2016--Present}{PhD Candidate}{Computer Science}
{Stanford University}{Stanford, CA}{
\emph{Advisor: Prof. Matei Zaharia.}
}{}

\cventry{2016--2018}{Master of Science}{Computer Science}
{Stanford University}{Stanford, CA}{
\emph{Advisor: Prof. Matei Zaharia.}
}{}

\cventry{2015--2016}{PhD Candidate}{Computer Science}
{Massachusetts Institute of Technology}{Cambridge, MA}{
\emph{Advisor: Prof. Matei Zaharia.} \\
\textbf{\emph{Transferred to Stanford University in Fall 2016 with advisor.}}
}{}

\cventry{2011--2014}{Bachelor of Science}{Computer Science and Engineering}
{University of California at Berkeley}{Berkeley, CA}{
\emph{Advisors: Profs. Scott Shenker and Sylvia Ratnasamy.}
}{}

\section{Teaching Experience}

\cventry{Winter 2018}{TA for CS 149 (Parallel Computing)}{Stanford University}{Stanford, CA}{} {}
\cventry{Winter 2017}{TA for CS 149 (Parallel Computing)}{Stanford University}{Stanford, CA}{} {}
\cventry{Fall 2014}{TA for CS 168 (Computer Networking)}{UC Berkeley}{Berkeley, CA}{} {}

\makeatletter
\renewcommand\@biblabel[1]{\textbullet}
\makeatother

\bibliographystyle{unsrt}
\nocite{*}
\bibliography{cv}

\section{Talks}

\cventry{August 2018}{Evaluating End-to-End Optimization for Data Analytics Applications in Weld}{VLDB 2018}{Rio de Janeiro, Brazil}{} {}
\cventry{August 2018}{Filter Before You Parse: Faster Analytics on Raw Data with Sparser}{VLDB 2018}{Rio de Janeiro, Brazil}{} {}
\cventry{June 2018}{Sparser: Fast Analytics over Raw Data by Avoiding Parsing}{Spark$+$AI Summit}{San Francisco, CA}{} {}
\cventry{April 2018}{Weld: Accelerating Data Science By 100$\times$}{DataEngConf SF}{San Francisco, CA}{} {}
\cventry{January 2018}{DIY Hosting for Online Privacy}{Stanford NetSeminar}{Stanford, CA}{} {}
\cventry{November 2017}{DIY Hosting for Online Privacy}{HotNets 2017}{Palo Alto, CA}{} {}
\cventry{October 2017}{Generating Fast Data Planes for Data-Intensive Systems}{HPTS 2017}{Asilomar, CA}{} {}
\cventry{September 2017}{Weld: Accelerating Data Science By 100$\times$}{Strate Data Conference}{New York, NY}{} {}
\cventry{March 2017}{Weld: An Optimizing Runtime for High-Performance Data Analytics}{Strata$+$HadoopWorld}{San Jose, CA}{} {}
\cventry{January 2017}{Weld: A Common Runtime for Data Analytics}{Stanford Platform Lab Seminar}{Stanford, CA}{} {}

\section{Industry Experience}

\cventry{Summer 2018}{Software Engineering Intern}{Databricks Inc.}{San Francisco, CA}{} {
\begin{itemize}
\item Worked on prototyping a new native code generation engine in Apache Spark.
\end{itemize}
}

\cventry{Summer 2016}{SWE Intern}{Google Inc.}{Mountain View, CA}{} {
\begin{itemize}
\item Studied and implemented several Conflict-Free Replicated Data Types
(CRDTs) on top of a P2P database called Syncbase.
\end{itemize}
}

\cventry{Summer 2014}{Undergraduate Researcher}{International Computer Science Institute}{Berkeley, CA}{} {
\begin{itemize}
\item Designed and implemented E2, a framework for effiently managing and deploying a NFV cluster
on commodity hardware.
\end{itemize}
}

\cventry{Summer 2013}{SDE Intern}{VMware Inc.}{Palo Alto, CA}{} {
\begin{itemize}
\item Developed and tested a distributed L7 Firewall in the VMware
ESX hypervisor kernel.
\end{itemize}
}

\cventry{Winter 2013}{Mobile Application Developer}{El Camino Hospital}{Mountain View, CA}{}{
\begin{itemize} 
\item Developed an iOS application for to coordinate a raffle at an event.
Integrated Amazon SimpleDB and Facebook Graph APIs.
\end{itemize}
}

\cventry{Summer 2012}{Software Engineering Intern}{Cooliris Inc.}{Palo Alto, CA}{} {
\begin{itemize} 
\item Designed and developed \emph{HashGallery}, an iOS client for Instagram,
Twitter, and Flickr image search.
\end{itemize}
}

\section{Honors and Awards}
\cventry{2016}{NSF GRFP Honorable Mention}{}{}{}{}
\cventry{2015--2016}{Jacobs Presedential Fellowship}{}{}{} {}


\section{References}
\cvdoublecolumn{\cvreference{Matei Zaharia}
    {Department of Computer Science}
    {Stanford University}
    {353 Serra Mall}
    {Stanford, CA 94035}
    {matei@cs.stanford.edu}
    {}
    }
    {\cvreference{Peter Bailis}
    {Department of Computer Science}
    {Stanford University}
    {353 Serra Mall}
    {Stanford, CA 94035}
    {pbailis@cs.stanford.edu}
    {}
    }

\end{document}
